Figures

### 2018-07-12 figures/08_maps.Rmd
add sample sizes to results table

# pull the lower partition group as an sf object
get_sub <- function(dt, col_name, split_value){
  coordinatize(
    dplyr::filter(dt, UQ(rlang::sym(as.character(col_name))) <= split_value), 
    "lat", "long")
}

lower_iws_maps <- lapply(which(partition_splits$scale == "iws"), 
                         function(x) {
                           nes_sub <- get_sub(nes_iws, 
                                            partition_splits[x, "iws_names"],
                                            partition_splits[x, "splits"])

>>>>

# pull the lower partition group as an sf object
lower_iws_maps <- lapply(which(partition_splits$scale == "iws"), 
                         function(x) {
                           nes_sub <- get_sub(nes_iws, 
                                            partition_splits[x, "iws_names"],
                                            partition_splits[x, "splits"])
